### 2016-07-13 docs/poster - smaller/poster.tex
Poster smaller

\documentclass[a0,landscape]{a0poster}
\usepackage[paperwidth=93in, paperheight=36in, textwidth=87in, textheight=30in, scale=2]{geometry}

@@

\begin{minipage}[b]{0.85\linewidth}
\VERYHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\[0.5cm] % Title
\Huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
\Huge Engineering \& Computer Science, Concordia University\\[0.5cm] % University/organization
\huge \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
\end{minipage}
%
\begin{minipage}[b]{0.19\linewidth}
\includegraphics[width=30cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}

@@

\begin{multicols}{5} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more

>>>>

\documentclass[a0,portrait]{a0poster}
\usepackage[paperwidth=36in, paperheight=59in, textwidth=30in, textheight=53in, scale=2]{geometry}

@@

\begin{minipage}[b]{0.85\linewidth}
\veryHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\[0.5cm] % Title
\huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
\huge Engineering \& Computer Science, Concordia University\\[0.5cm] % University/organization
\large \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
\end{minipage}
%
\begin{minipage}[b]{0.19\linewidth}
\includegraphics[width=20cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}

@@

\begin{multicols}{2} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more
